Statistical performance analysis of neural mass models?

### 2013-07-18 manuscript/manuscript.tex
minor edit
Working on comparing models
Merged changes to mansuscript
Code and figure for EKF benchmarking

\section{Introduction}

@@

e.g. EKF doesn't reach bound for model X, thus better algorithms are required.

\subsection{Effect of measurement noise? -- pretty boring}

e.g. scalp EEG vs iEEG?

@@

>>>>

\section{Introduction}
\label{sec:introduction}

@@

EKF doesn't reach bound for any nonlinear model, thus better algorithms are required.

\begin{figure}[ht]
  \begin{center}
    \includegraphics{./figures/pdf/CRBbar}
  \end{center}
  \caption{The mean squared error of the EKF against the BCRB for three models}
  \label{fig:CrbBar}
\end{figure}

@@

we say nothing about how algorithms will work with uncertainty in the actual model -- thus can be considered a ``best case'' situation, where we know the true model exactly.
